Annotation exploration for SCPCP000006, `predicted.score` threshold `r params$predicted.score_thr`

### 2024-11-13 analyses/cell-type-wilms-tumor-06/notebook/04_annotation_Across_Samples_exploration.Rmd
debugging to be able to run in CI if needed: We need to only loop over available samples, and not assume that all compartments are present when printing the count table

---
title: "Annotation exploration for SCPCP000006, `predicted.score` threshold `r params$predicted.score_thr`"
author: "Maud PLASCHKA"
date: "`r Sys.Date()`"
params: 
  predicted.score_thr: 0.85
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

```{r path_to_query}
sample_metadata_file <- file.path(repository_base, "data", "current", "SCPCP000006", "single_cell_metadata.tsv")

metadata <- read.table(sample_metadata_file, sep = "\t", header = TRUE) |>
  dplyr::filter(seq_unit != "spot")

# Create a data frames of all annotations
cell_type_df <- metadata$scpca_sample_id |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      # Read in the Seurat object
      srat <- readRDS(
        file.path(result_dir, sample_id, paste0("02b-fetal_kidney_label-transfer_", sample_id, ".Rds"))
      )

@@

```{r fig.width=25, fig.height=3, results='asis'}
compartment_df <- cell_type_df |>
  # count how many per compartment
  dplyr::count(organ, compartment) |>
  # make the table wide and use a value of 0 if a count is missing
  tidyr::pivot_wider(names_from = compartment, values_from = n, values_fill = 0) |>
  # order the columns how we want to show them
  dplyr::select(organ, fetal_nephron, stroma, endothelium, immune)

@@

```{r fig.width=25, fig.height=3, results='asis'}
compartment_df <- cell_type_df |>
  # count how many per compartment
  dplyr::count(sample_id, compartment) |>
  # make the table wide and use a value of 0 if a count is missing
  tidyr::pivot_wider(names_from = compartment, values_from = n, values_fill = 0) |>
  # order the columns how we want to show them
  dplyr::select(sample_id, fetal_nephron, stroma, endothelium, immune)

>>>>

---
title: "Annotation exploration for SCPCP000006, `predicted.score` threshold `r params$predicted.score_thr`"
author: "Maud PLASCHKA"
date: "`r Sys.Date()`"
params: 
  predicted.score_thr: 0.85
  sample_ids: ""
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

```{r path_to_query}
sample_metadata_file <- file.path(repository_base, "data", "current", "SCPCP000006", "single_cell_metadata.tsv")
metadata <- read_tsv(sample_metadata_file)

# Determine which sample ids to loop over, which differs if we are testing
if (params$sample_ids == "") {
  sample_ids <- metadata |>
    dplyr::filter(seq_unit != "spot") |>
    dplyr::pull(scpca_sample_id) |>
    unique()
} else {
  sample_ids <- stringr::str_split_1(params$sample_ids, ",")
  stopifnot(
    "Could not determine the sample_ids from the provided param value." =
      all(sample_ids %in% metadata$scpca_sample_id)
  )
}

# Create a data frames of all annotations
cell_type_df <- sample_ids |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      # Read in the Seurat object
      srat <- readRDS(
        file.path(result_dir, sample_id, paste0("02b-fetal_kidney_label-transfer_", sample_id, ".Rds"))
      )

@@

```{r fig.width=25, fig.height=3, results='asis'}
compartment_df <- cell_type_df |>
  # count how many per compartment
  dplyr::count(organ, compartment) |>
  # make the table wide and use a value of 0 if a count is missing
  tidyr::pivot_wider(names_from = compartment, values_from = n, values_fill = 0)

@@

```{r fig.width=25, fig.height=3, results='asis'}
compartment_df <- cell_type_df |>
  # count how many per compartment
  dplyr::count(sample_id, compartment) |>
  # make the table wide and use a value of 0 if a count is missing
  tidyr::pivot_wider(names_from = compartment, values_from = n, values_fill = 0)
